%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.1 (9/2/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Samuel }{Brandão}{Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Via Padova, 178
Milan, 20132 - Italy
+39 3894570300
~
\href{mailto:gb.samuel@gmail.com}{gb.samuel@gmail.com}
\href{http://it.linkedin.com/in/sambrandao}{linkedin.com/in/sambrandao}
\href{http://github.com/khamusa}{github.com/khamusa}
\href{http://bitbucket.org/khamusa}{bitbucket.org/khamusa}
\section{languages}
portuguese native
english fluency
italian fluency
\section{techs}
{\color{red} $\varheartsuit$} Ruby (\& Rails)
{\color{red} $\varheartsuit$} Python 3
PostgreSQL, MySQL
MongoDB
Git
JavaScript
Angular, JQuery
CSS3 \& HTML5
Heroku
AWS
Elastic Search
RabbitMQ
F\#
Erlang
\section{concepts}
{\color{red} $\varheartsuit$} Software Design
{\color{red} $\varheartsuit$} Agile development
{\color{red} $\varheartsuit$} Functional Programming
{\color{red} $\varheartsuit$} BDD Workflows
Database Design
Performance Optimization
MetaProgramming
\end{aside}

%----------------------------------------------------------------------------------------
%	ABOUT ME SECTION
%----------------------------------------------------------------------------------------

\section{summary}
Accomplished software engineer with 8+ years of experience building products (SaaS)
using a range of technologies including Ruby/Rails, Python and JavaScript with multiple frameworks, relational and NoSQL databases.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
\begin{entrylist}
\entry
{apr/2016-now}
{Lets.events}
{https://lets.events}
{\emph{Development \& Technical Leadership} \\
♦ Key participation in project management and technical decision making processes.\\
♦ Scrum Master / Implementation of Scrum methodology for the webapp development team.\\
♦ Full Stack Developer.
}
%------------------------------------------------
\entry
{apr/2015-2016}
{Senior Developer at 77Agency/Allin1Social}
{http://www.allin1social.com, Italy}
{
♦ Performed extensive bugfixing, reduced the legacy code complexity, improved
code design and quality according to every measurable metric. \\
♦ Reduced the time spent by support staff by creating tools that brought to
surface the most critical issues affecting the clients experience.\\
♦ Improved the data retrieval, integration and processing mechanism,
both by optimizing existing tasks and also by applying advanced heuristics,
which led to an 82\% reduction of the overall daily/hourly workload, and
a considerable service reliability boost.\\
♦ Main technologies used: Ruby / Rails, MongoDB, Redis, JS / ReactJS.
}
%------------------------------------------------
\entry
{2004-apr/2015}
{Freelance Developer}
{Brazil, Italy}
{\emph{Developer} \\ Worked as a Freelance Developer since 2004, having
worked with a coprehensive set of technologies, including Ruby, Python, PHP (using CodeIgniter, Wordpress, Magento), JS/CoffeeScript, AngularJs and ReactJs.
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\section{particular projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2012-2014}
{Miviro / Lead Developer}
{http://www.miviro.com.br}
{\emph{A social network/management tool for tour agencies} \\
% Miviro is , developed with
% Rails, HTML5, CSS3 and plenty of Javascript/Ajax.
}
%------------------------------------------------
\entry
{2011}
{Wertix CMS}
{Own project}
{\emph{Visual Content Management System} \\
% Wertix was a CMS developed from scratch as a mean to practice and learn
% the Ruby on Rails framework. The resulting application was surprisingly
% easy to use. Wertix taught me about the importance of a carefully thought UX.
% It employed a very interesting
%concept of page blocks. Every content type created could be either displayed in
%standalone mode (a gallery, for example) or as a page block, which could then be
%easily dragged-and-dropped to any position in any other page.
%The complexity of the system was on handling the polymorphic characteristics
%content types using relational databases (PostgreSQL).
}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}
\begin{entrylist}
%------------------------------------------------
\entry
{2011--2015}
{Bachelor {\normalfont of Computer Science, graduated \textit{cum laude}}}
{Università degli Studi di Milano}
{Laurea in Informatica}
%------------------------------------------------
%\entry
%{2007--2008}
%{Bachelor {\normalfont of Business Studies}}
%{The University of California, Berkeley}
%{Specialization in Commerce}
%------------------------------------------------
\end{entrylist}

\section{about me}
I started programming at the age of 11 and working professionaly at the age of 19.
While being a self-taught programmer contributed significantly to my problem
solving skills, completing my Bachelors Degree in Milan granted me a more
comprehensive view of the whole technological ecosystem. I worked on different
types of projects and teams, and have been focusing on SAAS products for the last
few years. I am naturally passionate about software development and I pursue
pragmatism on my work on a daily basis. I've also worked as a professional
theater actor in Brazil. I am a fan of cats, daily exercises and midfulness
meditation.
\end{document}